Future challenges for Research Software Engineering

### 2025-05-17 future_challenges_for_RSEng.tex
change verb, BE spelling

\begin{story}{Changes to the Universities}{changes}
Kim found work years ago at one of the first RSE units in Arcadia. After a couple of years he moved to the university of
Avalon which was interested in setting up their own department for RSEs in order to not fall behind the university of Arcadia.
Kim improves upon the model set forth by the University of Arcadia based on valuable experience. Since the university
of Avalon has to follow different rules, not everything can be straightforwardly adapted. Life would be so much easier
if at least university regulations would be homogenized, no?
\end{story}

>>>>

\begin{story}{Changes to the Universities}{changes}
Kim found work years ago at one of the first RSE units in Arcadia. After a couple of years he moved to the university of
Avalon which was interested in setting up their own department for RSEs in order to not fall behind the university of Arcadia.
Kim builds upon the model set forth by the University of Arcadia based on his valuable experience. Since the university
of Avalon has to follow different rules, not everything can be straightforwardly adapted. Life would be so much easier
if at least university regulations would be homogenised, no?
\end{story}
